---
title: "USA Earning per Capita by state (1969 - 1971)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: census.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
```

```{r}
# Customize My Own Theme
theme_violet <- theme(legend.key = element_rect(fill="yellow"),
           text = element_text(color="#9f5f86"),
           legend.background = element_rect(fill="#ece9f0"),
           plot.title = element_text(size=8),
           plot.subtitle = element_text(size=6),
           panel.background = element_rect(fill="#ece9f0"),
           panel.border = element_rect(fill=NA),
           panel.grid.minor.x = element_blank(),
           panel.grid.major.x = element_blank(),
           panel.grid.major.y = element_line(color="#cccccc", linetype=3),
           panel.grid.minor.y = element_blank(),
           plot.background = element_rect(fill="#ece9f0"),
           axis.text = element_text(color="#9f5f86", size=6.5),
           axis.title =  element_text(color="#9f5f86", size=7)
          )
```


```{r}
# Manipulating Datasets
statesdata <- data.frame(state.x77)
statesname <- data.frame(state.name)
region <- data.frame(state.region)
state <- cbind(statesdata, region,state.name)

state$epc <- state$Income/state$Population
state <- state[order(state$epc),]

state.w <- state[state$state.region =="West",]
state.s <- state[state$state.region =="South",]
state.nc <- state[state$state.region =="North Central",]
state.ne <- state[state$state.region =="Northeast",]
```

```{r}
# Create 1st the plot
plot1 <- ggplot(state, aes(x= reorder(state.name, epc), y=epc))+
  ylim(0,18)+
  geom_col(aes(fill=state$state.region), width=0.5)+
  labs(title="Earning Per Capita All State")+
  coord_flip()+
guides(fill = guide_legend(title = "State Region", title.position = "top", label.position = "left", label.hjust = 1))+
  labs(y="Earning per Capita", x="State Name
       ")+
  theme_violet


#ggplotly(plot1)
```


```{r}
# Create the 2nd plot
plot.west <- ggplot(state.w, aes(x=Population, y=Income))+
  ylim(3500,6500)+
  xlim(350,20000)+
  geom_point(aes(col=state.name, size=Income/Population), alpha=0.6, show.legend = F)+
  guides(size=F)+
  theme_violet

plot.south <- ggplot(state.s, aes(x=Population, y=Income))+
  ylim(3500,6500)+
  xlim(350,20000)+
  geom_point(aes(col=state.name, size=Income/Population), alpha=0.6, show.legend = F)+
  guides(size=F)+
  theme_violet

plot.nc <- ggplot(state.nc, aes(x=Population, y=Income))+
  ylim(3500,6500)+
  xlim(350,20000)+
  geom_point(aes(col=state.name, size=Income/Population), alpha=0.6, show.legend = F)+
  guides(size=F)+
  theme_violet

plot.ne <- ggplot(state.ne, aes(x=Population, y=Income))+
  ylim(3500,6500)+
  xlim(350,20000)+
  geom_point(aes(col=state.name, size=Income/Population), alpha=0.6, show.legend = F)+
  labs(title="Earning Per Capita by Region")+
  guides(size=F)+
  theme_violet

```



Column {data-width=550}
-----------------------------------------------------------------------


### All States

```{r}
ggplotly(plot1)
```

Column {data-width=500}
-----------------------------------------------------------------------

<h4><b>Earning per Capita = total income / total population</b></h4>
This visualization is based on <i>state.x77</i> dataset in R, which contains the USA 1971 census data.<br>
Findings from the graphs:<br>
- Alaska has highest earning per capita (high total income with few population).<br>
- Most of states with high earning per capita is located in west.

Here is the chart describing earning per capita for each region with comparisons to income and population.

### By Region

```{r}
subplot(
style(plot.west, showlegend = F),
style(plot.south, showlegend = F),
style(plot.nc, showlegend = F),
style(plot.ne, showlegend = F),
  nrows=2, shareX=T, shareY=T, widths=c(0.5, 0.5))
```


